---
title: "Mini-Project 1 Regression"
author: "Aaron"
date: "June 2, 2016"
output: 
  html_document: 
    highlight: haddock
    theme: cosmo
---

```{r message=F}
library(DAAG)
library(dplyr)
library(readr)
library(knitr)
library(magrittr)
```


### Synopsis

____________

#### What study will achieve?

In this assignment, I useed the R dataset `“litters”` (from the `DAAG` package) and create a regression model to predict brain weight.

####  Cite the data source

Data Description From DAAG Document

> Data on the body and brain weights of 20 mice, together with the size of the litter. Two mice were taken from each litter size.

> Wainright P, Pelkman C and Wahlsten D 1989. The quantitative relationship between nutritional effects on preweaning growth and behavioral development in mice. Developmental Psychobiology 22: 183-193.

### Methods

____________

#### Why (statistically) you can use the technique you choose?

I choose `regression` because it helps to fit a linear pattern through data. 

#### Explain the fields in the dataset

```{r}
glimpse(litters)
```

- `lsize`: litter size
- `bodywt`: body weight
- `brainwt`: brain weight

#### Explain/show your experimental setup (i.e. the r linear model)

As follow:

```{r}

litters %>% 
        lm(brainwt ~ lsize + bodywt, .) %>% summary()

```

### Analysis
____________

#### Show your final regression equation:

```{r}

litters %>% lm(brainwt ~ lsize + bodywt, .) -> fit_0

as.formula(
  paste0("brainwt ~ ", round(coefficients(fit_0)[1],4), " + ", 
    paste(sprintf("%.4f * %s", 
                  coefficients(fit_0)[-1],  
                  names(coefficients(fit_0)[-1])), 
          collapse=" + ")
  )
)

```

#### Show a diagram of your regression model vs. the data

```{r}
layout(matrix(c(1,2,3,4),2,2)) # optional 4 graphs/page 
plot(fit_0)
```

#### Discuss the quality of fit, explain what the diagram shows in terms of how to use it to predict

From the summary, quality of the fit is good, model explain **60.94%** variation of the data. 

We use the final equation to get the expected value of the **brain weight** by inputting the right `lsize` and `bodywt`


### Conclusion

____________

#### Explain what your experiment accomplished

Fit a very simple linear model over a very very small (20 obs) data, proved that litter size and body weight can predict the brain weights of the rats. 



